This report was requested by __`r paste(as.character(toupper(report_data_object()$firstname)), toupper(as.character(report_data_object()$lastname)), sep = " ")`__ to investigate the PPN n. __`r unique(as.character(report_data_object()$ppn))`__         


```{r Outbreak, warning=FALSE, message=FALSE, echo = FALSE, results='asis'}

outbreak <- subset(report_data_object()$result$farms_RT90,
                   report_data_object()$result$farms_RT90$Ppn == report_data_object()$ppn)

```

<br>

### 1. GEOGRAPHIC LOCATION

* The PPN under investigation is located in __`r toupper(paste(outbreak@data$Lan))`__ within the municipality of __`r toupper(paste(outbreak@data$Kommun))`__ 

* The address of the PPN is __`r toupper(paste(outbreak@data$Adress,",", outbreak@data$Postnummer, "", outbreak@data$Kommun))`__


```{r PlotMap1, warning=FALSE, message=FALSE, echo = FALSE, results='asis', fig.height=14, fig.width=14}

NUTS_03M <- report_data_object()$NUTS_03M[
            report_data_object()$NUTS_03M$STAT_LEVL_ == 3, 1:2]
NUTS_03M@data$Lan <- report_data_object()$result$nuts_label$Swedish[
                       match(as.character(NUTS_03M@data$NUTS_ID),
                             report_data_object()$result$nuts_label$NUTS)]


plot(NUTS_03M, axes=T)

# Account for points falling outside Swedish border
if(all(!is.na(over(outbreak, NUTS_03M)))){
lan <- over(outbreak,NUTS_03M)
lan <- NUTS_03M[NUTS_03M@data$NUTS_ID==lan$NUTS_ID,]
plot(lan, add=T, col="yellow")
}#else{
#   plot(1,1,col="white")
#   text(1,1,"provided coordinates fall outside Swedish borders")

points(outbreak, pch=19, col="red", cex=1)
invisible(text(coordinates(NUTS_03M),
               labels=as.character(NUTS_03M@data$Lan), 
               cex=0.8))
title(expression(paste("Geographic location of the PPN under investigation")))
legend("bottomright",
        cex=1.3, 
        "PPN location", 
        pch=19, 
        pt.cex = 1.2,
        col="red",
        bty="n")
```