This report was requested by __`r paste(as.character(toupper(report_data_object()$firstname)), toupper(as.character(report_data_object()$lastname)), sep = " ")`__ to investigate the PPN n. __`r unique(as.character(report_data_object()$ppn))`__         


```{r Outbreak, warning=FALSE, message=FALSE, echo = FALSE, results='asis'}

outbreak <- subset(report_data_object()$result$farms_RT90,
                   report_data_object()$result$farms_RT90$Ppn == report_data_object()$ppn)

```

<br>

### 1. GEOGRAPHIC LOCATION

* The PPN under investigation is located in __`r toupper(paste(outbreak@data$Lan))`__ within the municipality of __`r toupper(paste(outbreak@data$Kommun))`__ 

* The address of the PPN is __`r toupper(paste(outbreak@data$Adress,",", outbreak@data$Postnummer, "", outbreak@data$Kommun))`__


```{r }

NUTS_03M <- report_data_object()$NUTS_03M[
            report_data_object()$NUTS_03M$STAT_LEVL_ == 3, 1:2]
NUTS_03M@data$Lan <- report_data_object()$result$nuts_label$Swedish[
                       match(as.character(NUTS_03M@data$NUTS_ID),
                             report_data_object()$result$nuts_label$NUTS)]


plot(NUTS_03M, axes=T)
```